\documentclass[10pt,a4paper,ragged2e,withhyper]{class}
\geometry{margin=1.27cm,columnsep=0.75cm}

\usepackage{paracol}
\usepackage{multicol}
\usepackage{mfirstuc}
\usepackage{hyphenat}
\hyphenation{none}

\setmainfont{Roboto Slab}
\setsansfont{Lato}
\renewcommand{\familydefault}{\sfdefault}

\input{components/header.tex}

\begin{document}
\thispagestyle{empty}
\columnratio{0.3}

\makecvheader{}

\begin{paracol}{2}
    \sectionheading{Strengths}
    \strengthlist{Projects, Problem Solving, Teamwork and Collaboration, Adaptability, Time management, Experience with emerging technologies}


    \sectionheading{Achievements}
    \achievementlist{Solved 100+ DSA problems}


    \sectionheading{Skills}
    \skillsection{DSA, Flutter, Dart, React, Express, Rest API, SQL, GitHub, OOPs}{HTML, CSS, SCSS, JavaScript, TypeScript, MongoDB, Git, C++, Java}


    \sectionheading{Education}
    \begin{itemize}
        \item[\ding{117}]
        \education{B.Tech. Computer Science}{Poornima University}{Sep 2021\hspace{2 mm}-\hspace{2 mm}Present}{CGPA\hspace{1 mm}:\hspace{2 mm}8.64/10}
        \item[\ding{117}]
        \education{Senior Secondary Education}{Warren Academy School}{2020\hspace{2 mm}-\hspace{2 mm}2021}{Percentage\hspace{1 mm}:\hspace{2 mm}77\%}
        \item[\ding{117}]
        \education{Secondary Education}{Warren Academy School}{2018\hspace{2 mm}-\hspace{2 mm}2019}{Percentage\hspace{1 mm}:\hspace{2 mm}80\%}
    \end{itemize}


    \sectionheading{Certificates}
    \begin{itemize}
        \item[\ding{51}] \certificate{NPTEL}{Foundation of R Software}{https://drive.google.com/file/d/1I9DyGV1zhH12HAQF3N3Lb4lt6puVK38a/view?usp=drive_link}
        \item[\ding{51}] \certificate{NPTEL}{Programming in Modern C++}{https://drive.google.com/file/d/1Gn0N30TvQEilPlV0f6Vq84VdMZ6bnsIX/view?usp=drive_link}
    \end{itemize}


    \switchcolumn{}

    \sectionheading{About Me}
    \aboutme{\textbf{Fluent in Flutter and Dart} for building expressive, \textbf{feature-rich mobile applications}. Proven experience with a wide range of flutter packages and libraries to produce re-usable testable codebases.\\\textbf{Experienced in frontend development} using React, proficiency in JavaScript and TypeScript, and skilled in HTML, CSS, and SCSS.\\A \textbf{solid background in backend technologies} NodeJS, REST Api, Firebase. Self-starter keen to provide insights, grow with experienced minds, and craft forward-leading  solutions that improve user experience.}


    \sectionheading{Experience}
    \begin{itemize}
        \experience{Research and Development Intern}{Axis India Machine Learning}{May 2024}{June 2024}{Remote}{
            \begin{itemize}
                \item[\ding{84}] Developing and implementing state-of-the-art models for Computer Vision and Natural Language Processing.
                \item[\ding{84}] Deploying models into production using advanced MLOps principles to ensure scalability, reliability, and efficiency.
            \end{itemize}
        }
    \end{itemize}


    \sectionheading{Projects}
    \begin{itemize}
        \project{Sonicity}{https://github.com/AkshatGupta-30/Sonicity--Flutter}{Flutter}{
            \begin{itemize}
                \item[\footnotesize{\ding{109}}] \normalsize{A Flutter-based mobile application utilizing the JioSaavn API for an immersive audio experience, features modular architecture.}
                \item[\footnotesize{\ding{109}}] \normalsize{\textbf{Dependencies Used} \hspace{1.2mm}-\hspace{1.2mm} audioplayer, audio\_service, get, get\_it, http, just\_audio, shared\_preferences, sqflite, and many more…}
            \end{itemize}
        }
        \project{Chit-Chat-Pro}{https://github.com/AkshatGupta-30/Chit-Chat-Pro--Flutter}{Flutter}{
            \begin{itemize}
                \item[\footnotesize{\ding{109}}] \normalsize{Created a ChatGPT clone with enhanced features like text-to-speech, image-recognition, etc….}
                \item[\footnotesize{\ding{109}}] \normalsize{Used GetX State Management tool to enhance productivity and maintainability of application}
                \item[\footnotesize{\ding{109}}] \normalsize{\textbf{Libraries Used} \hspace{1.2mm}-\hspace{1.2mm} get, get\_it,http, flutter\_tts, speech\_to\_text, and many more…}
            \end{itemize}
        }
        \project{Chest x-ray Disease Classification}{https://github.com/AkshatGupta-30/Chest-X-Ray--DL}{Deep Learning}{
            \begin{itemize}
                \item[\footnotesize{\ding{109}}] \normalsize{Developed Chest X-ray Disease Classification system using Keras and TensorFlow.}
                \item[\footnotesize{\ding{109}}] \normalsize{Implemented transfer learning with VGG-16, VGG-19, and ResNet-50 for accurate disease localization.}
            \end{itemize}
        }
        \project{DevQuizzers}{.}{Mern}{%% TODO: Add link
            \begin{itemize}
                \item[\footnotesize{\ding{109}}] \hyphenation{}\normalsize{Developed online quiz web application using Mern stack with TypeScript.}
                \item[\footnotesize{\ding{109}}] \nobreak\normalsize{It provides a wide range of computer skills interview questions, allowing users to practice and assess their knowledge across various domains.}
            \end{itemize}
        }
        \projectongoing{Polling Day}{Mern}{
            \begin{itemize}
                \item[\footnotesize{\ding{109}}] \hyphenation{}\normalsize{An Online voting platform for elections.}
                \item[\footnotesize{\ding{109}}] \nobreak\normalsize{Register your own polling day to conduct elctions accross organization.}
            \end{itemize}
        }
    \end{itemize}
\end{paracol}

\end{document}